PInSoRo: A Dataset for Deep-Learning of Human-Robot Social Interactions

### 2017-06-28 paper.tex
Update on Overleaf.

Child-robot interactions are increasingly being explored in domains which
require longer-term applications, such as healthcare and education. In order
for a robot to behave in an appropriate manner over longer time scales, its
behaviours should be aligned and meaningful to the interacting children.
Generating such sustained and engaging social behaviours is an on-going research
challenge, and we argue here that the recent progress of deep machine learning
opens new perspectives that the Human-Robot Interaction (HRI) community
should embrace.

As an initial step in that direction, we introduce a novel,
open dataset of children social interactions, designed with
machine learning applications in mind. Our data acquisition methodology relies on
a engaging and purposefully underspecified \emph{free play} interaction. By doing
so, we capture a rich set of behavioural patterns occurring in natural
social interactions between children. Learning to recognise, and possibly generate, such
behaviours is one of the future research directions that we foresee this dataset to effectively support.

@@

The family of recurrent neural networks (RNNs) have repeatedly made the
headlines over the last few years with impressive results---notably in image
classification, image labelling and automatic translation. They have been
however largely ignored by other fields as they are perceived to require
impossibly large datasets (hundreds of thousands to millions of observations) to
actually build up useful capabilities.  Even though neural networks have
demonstrated compelling results in open-ended, under-specified tasks like image
labelling, they did not stand out as attractive approaches to problems involving
high dimensions with relatively small datasets available -- like human-robot
social interactions.  Besides, if one considers ``social interactions'' to also
entail joint behavioural dynamics, and therefore, some sort of temporal
modeling, neural networks look even less enticing as time is notably absent from
most of the tasks which neural networks have been successful at.

That being said, in 2015, the Google DeepMind team demonstrated how a convolutional
recurrent neural network could learn to play the game Break-Out (amongst
48 other Atari games) by only looking at the gaming console
screen~\cite{mnih2015human}. This result represents a major milestone: they showed
that a relatively small sample size (about 500 games) is sufficient for an 
artificial agent to not only learn how to play (which requires an implicit model 
of time to adequately move the Break-Out paddle), but to also create gaming 
strategies that look like they would necessitate planning (the system first
breaks bricks on one side to eventually get the ball to break-out and reach out the area
above the remaining bricks, therefore ensuring rapid progress in the
game).

More recently, Ogata's team~\cite{yang2017repeatable} has demonstrated how an
adequately configured RNN is able to learn a complex robotic task (folding soft
objects like towels using a dual-arm mobile manipulator) from only \emph{35}
demonstrations of $\approx$ 70 seconds-long teleoperated
sequences. The network inputs are the raw video stream from the head camera and the
12 degrees of freedom of the two arms. Successfully folding towels entails an explicit sequencing of
actions (therefore implicit temporal modeling). The fact that such a complex
process can be successfully learned from a small training dataset should lead
us to reconsider the range of domains to which RNNs would be applicable.

Indeed, as we have previously argued~\cite{lemaignan2016towards}, we believe
that the complexity of mechanisms that such neural networks have been able to
uncover and model should invite our community to explore its applicability to
human-robot interactions (HRI) in general, and sustained, natural child-robot
interactions in particular.
%However, the current lack of appropriate HRI
%datasets suitable for neural networks training is an obstacle. In this article
%we introduce the PInSoRo dataset, a large dataset of child-child natural
%interactions suitable for machine learning.

@@

The use of interaction datasets to teach robots how to socially behave has been
previously explored, and can be considered as the extension of the traditional
learning from demonstration (LfD) paradigms to social interactions
(i.e.,~\cite{nehaniv2007imitation,mohammad2015interaction}). However, existing
research focuses on low-level identification or generation of short,
self-standing behaviours, including social gestures~\cite{nagai2005learning} and
gazing behaviours~\cite{calinon2006teaching}.

@@

These examples show the burgeoning interest of our community for the automatic
learning of social interactions, but also highlight the lack of structured
research efforts, as further illustrated by the limited availability of large
and open datasets of social interactions, suitable for machine-learning
applications.

One such dataset is the \emph{Multimodal Dyadic Behavior Dataset}
(\emph{MMDB},~\cite{rehg2013decoding}). It comprises of 160 sessions of 3 to 5
minute child-adult interactions. During these interactions, the experimenter
plays with toddlers (1.5 to 2.5 years old) in semi-structured ways.  The dataset
includes video streams of the faces and the room, audio, physiological data
(electrodermal activity) as well as manual annotations of specific behaviours
(like gaze to the examiner, laughter, pointing). While this dataset is in
principle relevant, it focuses on very young children during short, adult-driven
interactions. As such, it does not include episodes of naturally-occurring
social interactions between peers, and the diversity of said interactions is
limited. Besides, the lack of intrinsic and extrinsic camera calibration
information in the dataset prevent the automatic extraction and labelling of key
interaction features (like mutual gaze).

Another recent dataset, the \emph{Tower Game Dataset}~\cite{salter2015tower},
focuses specifically on rich dyadic social interactions. The dataset comprises
of 39 adults recorded over a total of 112 annotated sessions of 3 min in
average. The participants are instructed to build a tower together with wooden
blocks. Interestingly, the participants are not allowed to talk to
maximise the amount of non-verbal communication. The skeletons and faces of the
participants are recorded, and the dataset is manually annotated with so-called
\emph{Essential Social Interaction Predicates} (ESIPs): rhythmic coupling
(entrainment or attunement), mimicry (behavioral matching), movement
simultaneity, kinematic turn taking patterns, joint attention. The dataset does
not appear to be publicly available on-line.

The PInSoRo dataset shares the aims of the \emph{Tower Game Dataset}, with
however a stronger focus on natural, real-world behaviours: as presented in the
following sections, we record much longer interactions (up to 40 minutes) of
free-play interaction, fostering a wider range of socio-cognitive behaviours.

\section{The Plymouth Interacting Social Robots Dataset (PInSoRo)}

The PInSoRo Dataset comprises of natural
social interactions arising between children, recorded with machine learning
and social robotics applications in mind. 
As detailed in section~\ref{availability}, this dataset is open and made freely
available to any interested researcher. It is intended to be used to train
machine-learning algorithms (typically, deep recurrent networks) to both
recognise and generate complex cognitive and social dynamics occurring in the
wild during social interactions.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.55\linewidth]{setup_child_child_top}
    \hspace{1em}
    \includegraphics[width=0.4\linewidth]{child-child-env}
    \caption{The free-play social interactions sandbox: two children interact in
    a free-play situation, by drawing and manipulating items on a touchscreen.
    Children are facing each other and sit on cushions. Each child wears a
    bright sport bib, either purple or yellow, to facilitate later
    identification.}

@@

The acquisition of such a dataset requires first the definition of a suitable
task for the participants to perform while they are recorded. The nature of
this task influences in fundamental ways the kind of interactions that might be
observed, and later, learned. Because they typically target specific social
or cognitive skills in a tightly controlled manner, traditional socio-cognitive tasks are
usually simple, constrained tasks that do not reflect the complexity and dynamics of
real-world interactions. Conversely, this dataset aims at capturing a rich set
of naturally-occurring social interactions, and participants should engage in a task that:
%CERE: this last sentence read a little oddly to me... not quite sure why to fix it though

\begin{itemize}
    \item is not directed, to maximise natural, non-contrived behaviours;
    \item elicit a large range of interaction situations;
    \item foster rich multi-modal interaction: simultaneous speech, gesture, and gaze
        behaviours are to be observed;
    \item evidence social dynamics, such as coupling, joint attention, turn-taking.
\end{itemize}

We have designed a new experimental task, called the \emph{freeplay sandbox}, that is based on 
free play interactions. Pairs of children (4-8 years old) are invited to freely draw and interact with items
displayed on an interactive table, without any explicit goal set by the experimenter (Fig.~\ref{fig|freeplay}).
The task is designed so that children can engage in open-ended and non-directive play, yet it is
sufficiently defined to be suitable for recording, and reproducible in comparable conditions.

@@

In order to constraint the dataset to a tractable domain, the task is limited to
a dyadic face-to-face interaction.  The resulting interaction space is
nevertheless high-dimensional, with two main axes: the game-related actions
(drawing, manipulating items, telling stories) and the social interactions
(monitoring the other's actions, discussing and agreeing on joint actions,
helping/hostile behaviours, etc.).

@@

The dataset consists of a collection of records. Each record correspond to one
play interaction between two children. To date (June 2017) 25 records have been
acquired (\ie 50 children), totalling 08h41m of recording. At the end of the acquisition campaign
(July 2017), the dataset is planned to include 50 records. As
the children decide themselves when to stop, the duration of each play episode varies ($M=20m51s,
SD=10m40s$). It is however capped to a maximum of 40 minutes.

@@

\paragraph{Hardware}
The sandtray is made of a 27" Samsung All-In-One computer running Ubuntu Linux
and equipped with a fast 1TB SSD hard-drive. The computer is held horizontally in
a custom aluminium frame standing 26cm above the ground
(visible in Fig.~\ref{fig|freeplay}). All the cameras are plugged directly over
USB-3 to the computer. The computer performs all the data acquisition using ROS
Kinetic.

The children faces are recorded from two short range Intel RealSense SR300
RGB-D cameras (0.2m to 1.2m) placed at the corners of the the sandtray
(Figs.~\ref{fig|rviz} and~\ref{fig|setup}) and tilted to face the children. The
cameras are rigidly mounted on custom 3D-printed brackets. This enables a
precise measurement of their 6D pose relative to the touchscreen (extrinsic
calibration).

@@

\paragraph{Software}
The sandbox is implemented with two frameworks: the Qt's QtQuick framework
for the graphical interface of the game, and the \emph{Robot Operating System}
(ROS) for the modular implementation of the data processing and data acquisition
pipelines. A dedicated bridge between QtQuick and ROS has been specifically
developed to enable the game interface to export the positions of every
interactive items as they move, the background image whenever it is painted over,
and the children's touches. The game interface is open-source and available online:
\url{https://github.com/severin-lemaignan/freeplay-sandbox-qt}.

@@

The experimental setup is visible in Fig.~\ref{fig|freeplay}, left.  The
experimenter stays in the room, visible to the child, during the whole
experiment. When requested by the nursery or school, another childminder
(nursery/school staff) can be present in the room. She/he is however asked not
to step in during the experiment. Not pictured on Fig.~\ref{fig|freeplay} is an
'ideas box', containing 5 cards depicting simple environments (zoo, forest,
city, space, pirates).  Children are invited by the experimenter to pick up a
card whenever they run out of activity ideas.

@@

We recruited normally developing children, from local primary schools and
nurseries. The children are aged 4 to 8 ($M=5.8$). So far, 50 children (23
female, 27 males) were recorded in pairs. Pairs were formed by the school or
nursery staff, and all the pairs knew each other beforehand.

@@

The following acquisition procedure has been followed with all participants. To
ease later identification, each child was given a colourful (purple or yellow)
sport bib to wear.

\newcommand{\tabitem}{~~\llap{\textbullet}~~}
    \begin{tabular}{@{}p{0.2\linewidth}p{0.8\linewidth}@{}}
\toprule
\bf Greetings                     & \tabitem explain the purpose of the study: showing robots how children play  \\
\emph{(about 5 min)}              & \tabitem briefly present a Nao robot: the robot stands up, gives a short
                                    message (\emph{"Hello, I'm Nao. Today, I'll be watching you while you
                                    play and soon I'll be able to play with you. Is that alright?"}), and
                                    sits down. The robot is then put aside and does not intervene
                                    for the remaining of the experiment \\
                                    %Condition B: "Hello, I'm Nao. Today I'll be playing with you. Exciting!")\\ 
                                  & \tabitem place children on cushions \\ 
                                  & \tabitem give them the yellow/purple sport
                                  bibs and make sure their hair is tied \\ 
                                  & \tabitem complete demographics on the tablet \\
                                  & \tabitem remind the children that they can withdraw at anytime \\ \midrule
\bf Visual focus task             & \emph{(unrelated visual task where children gaze at a moving target)}\\ 
\emph{(30 sec)}                   & \\ \midrule
\bf Tutorial                      & explain how to interact with the game, ensure the children are confident with the manipulation/drawing \\ 
\emph{(1-2 min)}                  & \\ \midrule
\bf Items placement game          & \emph{(unrelated task on spatial reasoning -- as this task uses the same graphical environment as the main free-play task, it helps the children to familiarise themselves with the game environment)} \\
\emph{(5 to 10 min)}              &  \\ \midrule
\bf Freeplay task                 & \tabitem initial prompt: \emph{"Just to remind you, you can use the animals or draw. Whatever you
                                  like. If you run out of ideas, there's also an ideas box. For example, the first one is a
                                  zoo. You could draw a zoo or tell a story. When you get bored or don't want to play
                                  anymore, just let me know."} \\
                                  & \tabitem let children play \\
                                  & \tabitem once they wish to stop, stop recording \\ \midrule
\bf Debriefing                    &  \tabitem answer possible questions from the children \\
\emph{(about 2 min)}              & \tabitem give stickers as a thank you \\ \bottomrule
\end{tabular}

@@

The dataset is freely available to any interested researcher\footnote{Note to
the reviewers: for the purpose of the review, an excerpt of the dataset is
available online: \url{https://freeplay-sandbox.github.io/}. A link to the
complete dataset will be made available in the final version of the article.}.
Due to ethical and data protection regulations, the dataset is however made
available in two forms: a public, Creative-Commons licensed, version that do
not include any video material of the children (no video streams, audio
included); and a complete version that includes all video streams. This second
version is freely available as well, but interested researchers must first fill
a data protection form.

>>>>

Child-robot interactions are increasingly being explored in domains which
require longer-term interactions, such as healthcare and education. In order
for a robot to behave in an appropriate manner over longer time scales, its
behaviours should be contingent and meaningful to the unfolding interaction.
Generating sustained and engaging social behaviours is an on-going research
challenge, and we argue here that the recent progress of deep machine learning
opens new perspectives that the Human-Robot Interaction (HRI) community
should embrace.

As an initial step in that direction, we introduce a novel,
open dataset of child social interactions, designed with
machine learning applications in mind. Our data acquisition methodology relies on
an engaging and purposefully underspecified \emph{free play} interaction. By doing
so, we capture a rich set of behavioural patterns occurring in natural
social interactions between children. Learning to recognise, and possibly generate, such
behaviours is one of the future research directions that we foresee this dataset to effectively support.

@@

The broad family of deep neural networks have repeatedly made the
headlines in the last few years with reports of impressive results---notably in image
classification, image labelling and automatic translation. They have been
however largely ignored by other fields as they are perceived to require
impossibly large datasets (hundreds of thousands to millions of observations) to
actually build up useful capabilities.  Even though neural networks have
demonstrated compelling results in non-trivial tasks like image
labelling, they did not stand out as attractive approaches to problems involving
high input and output dimensions where only relatively small datasets are available -- like human-robot
interactions.  Furthermore, if one considers ``social interactions'' to also
entail joint behavioural dynamics, and therefore, some sort of temporal
modeling, neural networks look even less enticing as time is notably absent from
most of the tasks which neural networks have been successful at.

That being said, in 2015, the Google DeepMind team demonstrated how a convolutional
recurrent neural network could learn to play the game Break-Out (amongst
48 other Atari games) by only looking at the gaming console
screen~\cite{mnih2015human}. This result represents a major milestone: they showed
that a relatively small sample size (about 500 games) is sufficient for an 
artificial agent to not only learn how to play (which requires an implicit model 
of time to adequately move the Break-Out paddle), but to also create gaming 
strategies that look like they would necessitate planning (the system first
breaks bricks on one side to eventually get the ball to break through and reach the area
above the remaining bricks, therefore ensuring rapid progress in the
game).

More recently, Ogata's team~\cite{yang2017repeatable} has demonstrated how an
adequately configured RNN is able to learn a complex robotic task (folding soft
objects like towels using a dual-arm mobile manipulator) from only \emph{35}
demonstrations of $\approx$ 70 second-long teleoperated
sequences. The network inputs are the raw video stream from the head camera and the
12 degrees of freedom of the two arms. Successfully folding towels entails an explicit sequencing of
actions (therefore implicit temporal modeling). The fact that such a complex
process can be successfully learned from a small training dataset should lead
us to reconsider the range of domains to which RNNs would be applicable.

%Indeed, as we have previously argued~\cite{lemaignan2016towards}, 
We believe
that the complexity of mechanisms that such neural networks have been able to
uncover and model should invite our community to explore its applicability to
human-robot interactions (HRI) in general, and sustained, natural child-robot
interactions in particular.
%However, the current lack of appropriate HRI
%datasets suitable for neural networks training is an obstacle. In this article
%we introduce the PInSoRo dataset, a large dataset of child-child natural
%interactions suitable for machine learning.

@@

The use of interaction datasets to teach robots how to socially behave has been
previously explored, and can be considered as the extension of the traditional
learning from demonstration (LfD) paradigms to social interactions
(i.e.,~\cite{nehaniv2007imitation,mohammad2015interaction}). However, existing
research focuses on low-level identification or generation of brief, autonomous behaviours, including social gestures~\cite{nagai2005learning} and
gazing behaviours~\cite{calinon2006teaching}.

@@

These examples show the burgeoning interest of our community for the automatic
learning of social responses, but also highlight the lack of structured
research efforts, as further illustrated by the limited availability of large
and open datasets of social interactions, suitable for machine-learning
applications.

One such dataset is the \emph{Multimodal Dyadic Behavior Dataset}
(\emph{MMDB},~\cite{rehg2013decoding}). It comprises of 160 sessions of 3 to 5
minute child-adult interactions. During these interactions, the experimenter
plays with toddlers (1.5 to 2.5 years old) in a semi-structured manner.  The dataset
includes video streams of the faces and the room, audio, physiological data
(electrodermal activity) as well as manual annotations of specific behaviours
(like gaze to the examiner, laughter, pointing). While this dataset is in
principle relevant, it focuses on very young children during short, adult-driven
interactions. As such, it does not include episodes of naturally-occurring
social interactions between peers, and the diversity of said interactions is
limited. Besides, the lack of intrinsic and extrinsic camera calibration
information in the dataset prevent the automatic extraction and labelling of key
interaction features (like mutual gaze).

Another recent dataset, the \emph{Tower Game Dataset}~\cite{salter2015tower},
focuses specifically on rich dyadic social interactions. The dataset comprises
of 39 adults recorded over a total of 112 annotated sessions of 3 min in
average. The participants are instructed to jointly construct a tower using wooden
blocks. Interestingly, the participants are not allowed to talk to
maximise the amount of non-verbal communication. The skeletons and faces of the
participants are recorded, and the dataset is manually annotated with so-called
\emph{Essential Social Interaction Predicates} (ESIPs): rhythmic coupling
(entrainment or attunement), mimicry (behavioral matching), movement
simultaneity, kinematic turn taking patterns, joint attention. The dataset does
not appear to be publicly available on-line.

The PInSoRo dataset shares the aims of the \emph{Tower Game Dataset}, with
however a stronger focus on natural, real-world behaviours: as presented in the
following sections, we record much longer interactions (up to 40 minutes) of
free-play interaction, capturing a wider range of socio-cognitive behaviours.

\section{The P[XXXXX] Interacting Social Robots Dataset (PInSoRo)}

The PInSoRo Dataset is comprised of natural
social interactions arising between children, recorded with machine learning
and social robotics applications in mind. 
As detailed in section~\ref{availability}, this dataset is open and made freely
available to any interested researcher. It is intended to be used to train
machine-learning algorithms (typically, deep recurrent networks) to both
recognise and generate complex cognitive and social dynamics occurring in the
wild during social interactions.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.55\linewidth]{setup_child_child_top}
    \hspace{1em}
    \includegraphics[width=0.4\linewidth]{child-child-env}
    \caption{The free-play social interactions sandbox: two children interact in
    a free-play situation, by drawing and manipulating items on a touchscreen.
    Children are facing each other and sit on cushions. Each child wears a
    bright sports bib, either purple or yellow, to facilitate later
    identification.}

@@

The acquisition of such a dataset requires a suitable
task for the participants to perform while they are being recorded. The nature of
this task influences in fundamental ways the kind of interactions that might be
observed, and later, learned. Because they typically target specific social
or cognitive skills in a tightly controlled manner, traditional socio-cognitive tasks are
usually simple, constrained tasks that do not reflect the complexity and dynamics of
real-world interactions. Conversely, this dataset aims at capturing a rich set
of naturally-occurring social interactions, and participants should engage in a task that:
%CERE: this last sentence read a little oddly to me... not quite sure why to fix it though

\begin{itemize}
    \item is not directed, to maximise natural, non-contrived behaviours;
    \item elicit a large range of interaction situations;
    \item foster rich multi-modal interaction, such as simultaneous speech, gesture, and gaze
        behaviours;
    \item evidence social dynamics, such as coupling, joint attention, turn-taking.
\end{itemize}

We have designed a new experimental task, called the \emph{freeplay sandbox}, that is based on 
free play interactions. Pairs of children (4-8 years old) are invited to freely draw and interact with items
displayed on an interactive table, without any explicit goal set by the experimenter (Fig.~\ref{fig|freeplay}).
The task is designed so that children can engage in open-ended and non-directive play, yet it is
sufficiently constrained to be suitable for recording, and allows the reproduction of social behaviour by an artificial agent in comparable conditions.

@@

In order to constrain the dataset to a tractable domain, the task is limited to
a dyadic face-to-face interaction.  The resulting interaction space is
nevertheless high-dimensional, with two main foci: the game-related actions
(drawing, manipulating items, telling stories) and the social interactions
(monitoring the other's actions, discussing and agreeing on joint actions,
supportive/antagonistic behaviours, etc.).

@@

The dataset consists of a collection of records. Each record correspond to one
play interaction between two children. To date (June 2017) 25 records have been
acquired (\ie 50 children), totalling 08h41m of recording. At the end of the acquisition campaign
(July 2017), the dataset is planned to include 50 records. As
the children decide themselves when to stop, the duration of each play episode varies ($M=20m51s,
SD=10m40s$). It is however capped at a maximum of 40 minutes.

@@

\paragraph{Hardware}
The sandtray is made of a 27" Samsung All-In-One computer running Ubuntu Linux
and equipped with a fast 1TB SSD hard-drive. The computer is held horizontally in
a custom aluminium frame standing 26cm above the floor
(visible in Fig.~\ref{fig|freeplay}). All the cameras are plugged directly over
USB-3 to the computer. The computer performs all the data acquisition using ROS
Kinetic.

The children's faces are recorded using two short range Intel RealSense SR300
RGB-D cameras (0.2m to 1.2m) placed at the corners of the the sandtray
(Figs.~\ref{fig|rviz} and~\ref{fig|setup}) and tilted to face the children. The
cameras are rigidly mounted on custom 3D-printed brackets. This enables a
precise measurement of their 6D pose relative to the touchscreen (extrinsic
calibration).

@@

\paragraph{Software}
The sandbox is implemented using two software frameworks: the Qt's QtQuick framework
for the graphical interface of the game, and the \emph{Robot Operating System}
(ROS) for the modular implementation of the data processing and data acquisition
pipelines. A dedicated bridge between QtQuick and ROS has been specifically
developed to enable the game interface to export the positions of every
interactive items as they move, the background image whenever it is painted over,
and the children's touches. The game interface is open-source and available online:
\url{https://github.com/severin-lemaignan/freeplay-sandbox-qt}.

@@

The experimental setup is shown in Fig.~\ref{fig|freeplay}, left.  The
experimenter stays in the room, visible to the child, during the whole
experiment. When requested by the nursery or school, another childminder
(nursery/school staff) can be present in the room. She/he is however asked not
to step in during the experiment. Not pictured on Fig.~\ref{fig|freeplay} is an
'ideas box', containing 5 cards depicting simple environments (zoo, forest,
city, space, pirates).  Children are invited by the experimenter to pick up a
card whenever they run out of activity ideas.

@@

We recruited typically developing children, from local primary schools and
nurseries. The children are aged 4 to 8 ($M=5.8$). So far, 50 children (23
female, 27 males) were recorded in pairs. Pairs were formed by the school or
nursery staff, and all the pairs knew each other beforehand.

@@

The following acquisition procedure has been followed with all participants. To
ease later identification, each child was given a brightly coloured (purple or yellow)
sports bib to wear.

\newcommand{\tabitem}{~~\llap{\textbullet}~~}
    \begin{tabular}{@{}p{0.2\linewidth}p{0.8\linewidth}@{}}
\toprule
\bf Greetings                     & \tabitem explain the purpose of the study: showing robots how children play  \\
\emph{(about 5 min)}              & \tabitem briefly present a Nao robot: the robot stands up, gives a short
                                    message (\emph{"Hello, I'm Nao. Today, I'll be watching you while you
                                    play and soon I'll be able to play with you. Is that alright?"}), and
                                    sits down. The robot is then put aside and does not intervene
                                    for the remaining of the experiment \\
                                    %Condition B: "Hello, I'm Nao. Today I'll be playing with you. Exciting!")\\ 
                                  & \tabitem place children on cushions \\ 
                                  & \tabitem give them the yellow/purple sports
                                  bibs and make sure their hair is tied \\ 
                                  & \tabitem complete demographics on the tablet \\
                                  & \tabitem remind the children that they can withdraw at anytime \\ \midrule
\bf Visual focus task             & \emph{(unrelated visual task where children gaze at a moving target)}\\ 
\emph{(30 sec)}                   & \\ \midrule
\bf Tutorial                      & explain how to interact with the game, ensure the children are confident with the manipulation/drawing \\ 
\emph{(1-2 min)}                  & \\ \midrule
\bf Items placement game          & \emph{(unrelated task on spatial reasoning -- as this task uses the same graphical environment as the main free-play task, it helps the children to familiarise themselves with the game environment)} \\
\emph{(5 to 10 min)}              &  \\ \midrule
\bf Freeplay task                 & \tabitem initial prompt: \emph{"Just to remind you, you can use the animals or draw. Whatever you
                                  like. If you run out of ideas, there's also an ideas box. For example, the first one is a
                                  zoo. You could draw a zoo or tell a story. When you get bored or don't want to play
                                  anymore, just let me know."} \\
                                  & \tabitem let children play \\
                                  & \tabitem once they wish to stop, stop recording \\ \midrule
\bf Debriefing                    &  \tabitem answer possible questions from the children \\
\emph{(about 2 min)}              & \tabitem give stickers as a thank you \\ \bottomrule
\end{tabular}

@@

The dataset is freely available to any interested researcher\footnote{Note to
the reviewers: for the purpose of the review, an excerpt of the dataset is
available online: \url{https://freeplay-sandbox.github.io/}. A link to the
complete dataset will be made available in the final version of the article.}.
Due to ethical and data protection regulations, the dataset is however made
available in two forms: a public, Creative Commons licensed, version that does
not include any video material of the children (no video streams, audio
included); and a complete version that includes all video streams. This second
version is freely available as well, but interested researchers must first fill
a data protection form.
